\Large{Research Seminar Software Science} \\ \huge{Simulation of monadic effects in Haskell}

### 2018-06-13 paper.tex
modified algebraic data types section

    In order to parse any of the statements of this simple programming language, an algebraic data type type namely \textbf{AST} needs to be created. This \textbf{AST} will provide a tree representation of the abstract structure of the programming language. The \textit{Abstract Syntax Tree} is illustrated below:

@@

    \noindent Additionally the definition of the \textbf{Operator} and \textbf{Condition} data types has been defined:

@@

>>>>

    In order to parse any of the statements of this simple programming language, an algebraic data type type namely \textbf{AST} needs to be created. This \textbf{AST} will provide a tree representation of the abstract structure of the programming language. The \textit{Abstract Syntax Tree} is portrayed through Haskell's algebraic data types and its implementation is illustrated below:

@@

    \noindent As it can be seen, the AST is referencing two data types which have not been created yet. As a consequence, the definition of the \textbf{Operator} and \textbf{Condition} data types has been defined below:

@@

    \subsection{Tokenizer}
